Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-18 paper.tex
Algo

\begin{proposition}
	We argue that a good choice for the functions $\theta_k$ may be constructed as follows. Pick a target parameter $\theta_0 \in [1;2)$, and a small $\delta>0$.
	Define the function $\theta_k^*$ as:
	\begin{equation}
	\theta_k^*(\gamma) = \sup \left\{\omega \in [1;2]  \mid \varphi_\omega\left(\min \frac{A_k \gamma}{\mu^k}\right) \ge 0 \right\} .
	\end{equation}
	Then the function
	\begin{equation}
	\label{eq:theta_k}
	\theta_k(\gamma) = \min(\max(1,\theta_k^*(\gamma)-\delta),\theta_0)
	\end{equation}
	is continuous, and verifies condition (\ref{eq:cond_theta_k}).
\end{proposition}
This construction has several advantages.
One is that it allows to choose arbitrarily the parameter $\theta_0$ that will be used asymptotically. A heuristic for this choice is proposed in section \ref{section:local}.
But it is also an easy approach to having an adaptive method, as the approximation of $\theta_k^*$ has a negligible cost (it only depends on the smallest value of $\frac{A_k \gamma}{\mu^k}$, and the function to invert is decreasing and concave).
We will show later on that this is often an excellent choice in practice.
\begin{proof}
	Since the partial derivative of $\frac{\partial\varphi_\omega(x)}{\partial\omega}$ is nonzero for any $x<1$, the implicit function theorem proves the continuity of $\theta_k^*$.
	The function $\theta_k^*(\gamma)$ is constructed so that every term in relation (\ref{eq:kl_diff_scal}) is non-negative.
	Therefore, by lemma \ref{lemma:F_P_theta}, using parameter $\theta_k^*(\gamma)-\delta$ ensures the strong decrease (\ref{eq:cond_theta_k}) of the Lyapunov function.
	It is no problem to constrain it to $[1,\theta_0]$, as using 1 always validates the inequality (\ref{eq:cond_theta_k}), and using $\theta_0$ when it is smaller than $\theta_k^*(\gamma)$ does as well.
\end{proof}

>>>>

\begin{proposition}
	We argue that a good choice for the functions $\theta_k$ may be constructed as follows. Pick a target parameter $\theta_0 \in [1;2)$, and a small $\delta>0$.
	Define the function $\theta_k^*$ as:
	\begin{equation}
	\theta_k^*(\gamma) = \sup \left\{\omega \in [1;2]  \mid \varphi_\omega\left(\min \frac{A_k \gamma}{\mu^k}\right) \ge 0 \right\} .
	\end{equation}
	Then the function
	\begin{equation}
	\label{eq:theta_k}
	\theta_k(\gamma) = \min(\max(1,\theta_k^*(\gamma)-\delta),\theta_0)
	\end{equation}
	is continuous, and verifies condition (\ref{eq:cond_theta_k}).
\end{proposition}
This construction has several advantages.
One is that it allows to choose arbitrarily the parameter $\theta_0$ that will be used asymptotically. A heuristic for this choice is proposed in section \ref{section:local}.
But it is also an easy approach to having an adaptive method, as the approximation of $\theta_k^*$ has a negligible cost (it only require to solve a one dimensional problem that depends on the smallest value of $\frac{A_k \gamma}{\mu^k}$, and the corresponding function to invert is decreasing and concave).
We will show later on that this is often an excellent choice in practice.
\begin{proof}
	Since the partial derivative of $\frac{\partial\varphi_\omega(x)}{\partial\omega}$ is nonzero for any $x<1$, the implicit function theorem proves the continuity of $\theta_k^*$.
	The function $\theta_k^*(\gamma)$ is constructed so that every term in relation (\ref{eq:kl_diff_scal}) is non-negative.
	Therefore, by lemma \ref{lemma:F_P_theta}, using parameter $\theta_k^*(\gamma)-\delta$ ensures the strong decrease (\ref{eq:cond_theta_k}) of the Lyapunov function.
	It is no problem to constrain it to $[1,\theta_0]$, as using 1 always validates the inequality (\ref{eq:cond_theta_k}), and using $\theta_0$ when it is smaller than $\theta_k^*(\gamma)$ does as well.
\end{proof}
